Model LF

### 2022-12-15 Paper version rmd.Rmd
commit

COMMENT> 
BEHAVIORAL> shock_kuld
TSRANGE 2005 3 2017 4
EQ> TSDELTALOG(shock_kuld) =  a_5* log(TSLAG(komp_r,1)) + a_6* log(TSLAG(shock_kuld,1)) + a_7*d_2013q1
COEFF> a_5 a_6 a_7
STORE> coe(17)

@@

COMMENT> tilføjet
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*kuld
IF>  shock_kuld_model <= 0
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*shock_kuld
IF>  shock_kuld_model > 0

>>>>

COMMENT> 
BEHAVIORAL> kuld
TSRANGE 2005 3 2017 4
EQ> TSDELTALOG(kuld) =  a_5* log(TSLAG(komp_r,1)) + a_6* log(TSLAG(kuld,1)) + a_7*d_2013q1
COEFF> a_5 a_6 a_7
STORE> coe(17)

@@

COMMENT> tilføjet
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*kuld
